A Short and Mechanized Consistency Proof for a Dependent Type Theory

### 2023-12-19 paper/paper.tex
Add figures for specification

\section{Specification of a Dependent Type Theory}
\label{sec:spec}
In this section, we present the dynamics and statics of the
dependent type theory whose logical consistency will be proven in
Section~\ref{sec:logrelproof}. For concision, we refer to this system
as \lang.

>>>>

\section{Specification of a Dependent Type Theory}
\label{sec:spec}

\begin{figure}[h]
\[
\begin{array}{lcll}
\mathit{Natural\ numbers}\\
[[i]],[[j]],[[n]] & ::= & [[0]]\ |\ [[S i]] & \mbox{zero, successor} \\ \\

\mathit{Contexts}\\
[[G]]       & ::= & [[empty]]\ |\ [[G ++ A]] &  \\ \\
\mathit{Terms}\\
[[a]],[[b]],[[c]],[[t]],[[p]],[[A]],[[B]] & ::= & [[Set i]]\ |\ [[i]]\  |\ [[Void]]
                  & \mbox{universes, variables, empty type} \\
            & |   & [[Pi A B]]\ |\ [[\ A a]]\ |\ [[a b]]
                  & \mbox{function types, abstractions, applications} \\
            & |   & [[a ~ b : A ]]\ |\  [[refl]]\ |\ [[J t a b p]]
                  & \mbox{equality types, reflexivity proof, J eliminator} \\
            & |   & [[Bool]]\ |\  [[true]]\ |\  [[false]]\ |\  [[if a b0 b1]]
                  & \mbox{boolean type, true, false, if}
\end{array}
\]
  \caption{Syntax of \lang}
  \label{fig:syntax}
\end{figure}

\begin{figure}[h]
\drules[P]{$[[a => b]]$}{Parallel Reduction}{Var, Set, Void, Pi, Abs, App, AppAbs, True, False, If, IfTrue, IfFalse, Bool, Eq, Refl, J, JRefl}
\drules[PS]{$[[a =>+ b]]$}{Transitive Closure of Parallel Reduction}{One, Step}
\drules[C]{$[[a <=> b]]$}{Coherence}{Intro}
\caption{Parallel reduction and coherence}
\label{fig:par}
\end{figure}

\begin{figure}[h]
\drules[Ctx]{$[[ |- G]]$}{Context Well-Formedness}{Empty, Cons}
\drules[T]{$[[G |-  a : A]]$}{Typing}{Var, Set, Pi, Abs, App, Conv, Refl, J, Bool, True, False, If, Void}
\caption{Syntactic typing for \lang}
\label{fig:typing}
\end{figure}

In this section, we present the dynamics and statics of the
dependent type theory whose logical consistency will be proven in
Section~\ref{sec:logrelproof}. For concision, we refer to this system
as \lang.
